Syntax and Semantics of Abstract Binding Trees

### 2015-11-11 paper.tex
[paper] describe morphism via commuting diagram

The interpretation of operator applications is most complicated. Recall that,
unlike in standard treatments of universal algebra, our operators are indexed
by symbol collections; therefore, operators must pass through suitable
renamings in order to be used in the interpretation. Let us begin by
constructing for each operator $\IsOperator{\Upsilon}{\vartheta}{a}$ the
morphism
$\Of{\SemBrackets{\vartheta}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
\to\Operators_{a}}$, which shall rename the parameters of the operator using
the environment. The natural transformation $\SemBrackets{\vartheta}_P$ is the
following composite:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_2}"]
    \& {\IMode{S^{\{\Upsilon\}}}} \arrow[r, "\IMode{\FLift{\pi_{(-)}}{}}"]
    \&[1.5em] {\IMode{\Operators_a}}
  \end{tikzcd}
\]

>>>>

The interpretation of operator applications is most complicated. Recall that,
unlike in standard treatments of universal algebra, our operators are indexed by
symbol collections; therefore, operators must pass through suitable renamings in
order to be used in the interpretation. Let us begin by constructing for each
operator $\IsOperator{\Upsilon}{\vartheta}{a}$ the morphism
$\SemBrackets{\vartheta}_P$ which shall rename the parameters of the operator
using the environment:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    |[alias = Src]|
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[r, swap, "\IMode{\pi_2}"]
    \&
    {\IMode{S^{\{\Upsilon\}}}}
      \arrow[r, swap, "\IMode{\FLift{\pi_{(-)}}{}}"]
    \&[1.5em]
    |[alias = Tgt]|
    {\IMode{\Operators_a}}
    \arrow[from = Src, to = Tgt, bend left, dashed, "\IMode{\SemBrackets{\vartheta}_{P}}"]
  \end{tikzcd}
\]
